Graphical Tests for Power Comparison of Competing Designs

### 2012-03-30 experiment-two.tex
discussion of second experiment: time and confidence

\subsection{Comparing Distributions}
\begin{figure*}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{power-exp2} 
   \caption{Overview of power predictions for the four different designs. The fully saturated thick lines show average predicted power for each of the designs facetted by size of the red group (top to bottom) and relative size of the blue group to the red group (left to right). }
   \label{fig:power2}
\end{figure*}

Since each participant provides results from nine lineups, we can use a generalized linear mixed effects model of power and account for individuals' abilities by including a subject-specific random intercept. We included all of the above described covariates  in the model, both as main effects and as two-way interaction with the design to assess their impact on the power of each of the designs.
Figure \ref{fig:power2} summarizes the modeling results as shown in table \ref{tbl:power2}. Generally we can see that the power of all four designs increases with an increase in effect size ($x$ axis), as well as an increase in sample size (top to bottom facetting). Depending on visualization setup, different designs have highest power: boxplots  are an alround good choice in visualizing a mean shift in a distribution. For small overall sample size dotplots (green dots and lines) show good power, but they  start to lose their advantage in favor of more summarized plots, such as density charts or histograms. Following the predicted power for density charts for the different ratios between the groups, we see that from left to right the density line does not benefit from additional information in the second group, unlike all of the other designs. Dotplots are the only design, in which each observation is shown individually. This increase in visual complexity might be the reason behind this phenomenon.

Density charts profit the most from an increase in sample size - making them particularly good design choices for a larger sample sizes.
\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & $z$ value & $p$-value \\ 
  \hline
(Intercept) & -3.11 & 0.41 & -7.61 & 0.00 \\ 
  density & 0.05 & 0.57 & 0.09 & 0.93 \\ 
  dotplot & 0.46 & 0.57 & 0.81 & 0.42 \\ 
  histogram & 0.06 & 0.58 & 0.11 & 0.91 \\ 
  d & 1.77 & 0.34 & 5.18 & 0.00 \\ 
  n1 & 0.02 & 0.00 & 9.73 & 0.00 \\ 
  ratio & 0.84 & 0.33 & 2.56 & 0.01 \\ 
  density:d & -0.60 & 0.47 & -1.27 & 0.20 \\ 
  dotplot:d & 0.03 & 0.46 & 0.07 & 0.95 \\ 
  histogram:d & -0.28 & 0.48 & -0.59 & 0.56 \\ 
  density:n1 & -0.00 & 0.00 & -0.36 & 0.72 \\ 
  dotplot:n1 & -0.01 & 0.00 & -3.00 & 0.00 \\ 
  histogram:n1 & -0.01 & 0.00 & -2.64 & 0.01 \\ 
  density:ratio & -0.28 & 0.47 & -0.59 & 0.56 \\ 
  dotplot:ratio & -1.01 & 0.46 & -2.19 & 0.03 \\ 
  histogram:ratio & -0.28 & 0.47 & -0.59 & 0.55 \\ 
   \hline
\end{tabular}
\end{center}
\caption{Results from a Generalized Linear Mixed Effects Model of Power of a lineup given design and all two-way interactions with effect size $d$, group size $n_1$, and ratio to second to first group size. The model was fit based on 2513 lineup evaluations of 208 participants.}
\label{tbl:power2}
\end{table}

\begin{table}[ht]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std..Error & t.value & pval \\ 
  \hline
(Intercept) & 3.85 & 0.09 & 42.21 & 0.00 \\ 
  density & 0.01 & 0.12 & 0.07 & 0.94 \\ 
  dotplot & 0.03 & 0.12 & 0.26 & 0.80 \\ 
  histogram & 0.23 & 0.12 & 1.97 & 0.05 \\ 
  d & -0.23 & 0.08 & -3.02 & 0.00 \\ 
  n1 & 0.00 & 0.00 & 1.74 & 0.08 \\ 
  I(n1/n2) & -0.04 & 0.02 & -1.48 & 0.14 \\ 
  density:d & 0.11 & 0.11 & 1.02 & 0.31 \\ 
  dotplot:d & 0.20 & 0.11 & 1.86 & 0.06 \\ 
  histogram:d & -0.01 & 0.11 & -0.09 & 0.93 \\ 
  density:n1 & -0.00 & 0.00 & -2.15 & 0.03 \\ 
  dotplot:n1 & -0.00 & 0.00 & -2.87 & 0.00 \\ 
  histogram:n1 & -0.00 & 0.00 & -0.93 & 0.35 \\ 
  density:I(n1/n2) & 0.04 & 0.03 & 1.18 & 0.24 \\ 
  dotplot:I(n1/n2) & 0.02 & 0.03 & 0.65 & 0.52 \\ 
  histogram:I(n1/n2) & 0.00 & 0.04 & 0.04 & 0.97 \\ 
   \hline
\end{tabular}
\end{center}
\caption{log time taken}

\end{table}

>>>>

\subsection{Comparing Distributions}
\begin{figure*}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{power-exp2} 
   \caption{Overview of power predictions for the four different designs. The fully saturated thick lines show average predicted power for each of the designs facetted by size of the red group (top to bottom) and relative size of the blue group to the red group (left to right). Thin lines represent variability due to subject-specific abilities. }
   \label{fig:power2}
\end{figure*}

Since each participant provides results from nine lineups, we can use a generalized linear mixed effects model of power and account for individuals' abilities by including a subject-specific random intercept. We included all of the above described covariates  in the model, both as main effects and as two-way interaction with the design to assess their impact on the power of each of the designs.
Figure \ref{fig:power2} summarizes the modeling results as shown in table \ref{tbl:power2}. Generally we can see that the power of all four designs increases with an increase in effect size $d$ (on the $x$ axis), as well as an increasing sample size $n_1$ (top to bottom facetting). Generally, an increase of the second group also is beneficial to power. Unlike all of the other designs,  dotplots actually lose power significantly as the second group increases. 
The reason behind this phenomenon might be visual complexity: dotplots are the only design that show individuals. With an increase in group size, visual complexity increases with it, which could hamper the observer in evaluating shifts.

The two highly summarized designs benefit the most from an increase in sample size: both density charts and boxplots profit significantly more than histograms and dotplots. This might, again, be a hint towards a trade-off between visual complexity and amount of information shown as basis for decisions. 
\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\begin{tabular}{lrrrrrl}
  \hline
& & Estimate & Error & $t$-value & \multicolumn{2}{l}{approx $p$-value} \\   \hline
\\[-8pt]
\bf design& Intercept & -3.11 & 0.41 & -7.61 & 0.00 & ***\\ 
&  density & 0.05 & 0.57 & 0.09 & 0.93 \\ 
 & dotplot & 0.46 & 0.57 & 0.81 & 0.42 \\ 
  &histogram & 0.06 & 0.58 & 0.11 & 0.91 \\ [2pt]
\multicolumn{2}{l}{\bf covariates}\\
&  d & 1.77 & 0.34 & 5.18 & 0.00 & ***\\ [1pt]
&   n1$_{100}$ & 1.84 & 0.19 & 9.73 & 0.00 & *** \\ [1pt]
&  ratio & 0.84 & 0.33 & 2.56 & 0.01 & ** \\ [2pt]
\multicolumn{2}{l}{\bf interactions}\\
&    density:d & -0.60 & 0.47 & -1.27 & 0.20 \\ 
&    dotplot:d & 0.03 & 0.46 & 0.07 & 0.95 \\ 
&    histogram:d & -0.28 & 0.48 & -0.59 & 0.56 \\ [1pt]
&    density: n1$_{100}$ & -0.10 & 0.26 & -0.36 & 0.72 \\ 
&    dotplot: n1$_{100}$ & -0.77 & 0.26 & -3.00 & 0.00 & *** \\ 
&    histogram: n1$_{100}$ & -0.69 & 0.26 & -2.64 & 0.01 & ** \\ [1pt]
&    density:ratio & -0.28 & 0.47 & -0.59 & 0.56 \\ 
&    dotplot:ratio & -1.01 & 0.46 & -2.19 & 0.03 & * \\ 
&histogram:ratio & -0.28 & 0.47 & -0.59 & 0.55 \\ 
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}}
\end{center}
\caption{Results from a Generalized Linear Mixed Effects Model of Power of a lineup given design and all two-way interactions with effect size $d$, group size $n_1$, and ratio to second to first group size. Reference group for all effects are boxplot designs. The model was fit based on 2513 lineup evaluations of 208 participants. Note that estimate and error for all terms involving $n_1$ are multiplied by a factor of 100.}
\label{tbl:power2}
\end{table}

Table \ref{tbl:speed2} gives an overview of results from a linear model for (log) evaluation time of lineups. Subject-specific speed (due to spatial ability) are accounted for  including a random intercept. Structurally, the model is the same as before, i.e. we regard effect size $d$, size $n_1$ of the first group, and the ratio $n_2/n_1$ between group sizes both as main effects and in two-way interactions with the four competing designs. To make estimate sizes comparable, we have again multiplied all estimates and standard errors involving the group size $n_1$ by 100. This means that we need to interpret those  estimates as average change if the group size is increased by 100 elements. 
The results of this model are similar to the previous: evaluation speeds needed for the four different designs is very close, but  histograms take on average a significantly longer time ($e^{0.23} = 1.26$ seconds) to evaluate than lineups of boxplots. 
Where an increase of sample size led to an increase of accuracy before, we now see that it increases time for evaluation of boxplot slightly, but not significantly so. What is interesting is that evaluation time decreases significantly with an increase in sample size, particularly for dotplots, but also for density charts. This is counter-intuitive to our previous argument on dotplots being affected by visual complexity the most. It seems, that observers of dotplot lineups come to a conclusion faster as sample size increases, albeit more often to  the wrong conclusion. Rather than visual complexity, this might be indicative that over-plotting is problematic in dotplots. While we tried to accommodate for over-plotting by making use of alpha-blending and jittering, this might not have been sufficient for the large sample size.

\begin{table}[ht]
\begin{center}
\resizebox{\linewidth}{!} {
\begin{tabular}{lrrrrrl}
  \hline
& & Estimate & Error & $t$-value & \multicolumn{2}{l}{approx $p$-value} \\   \hline
\\[-8pt]
\bf design& Intercept & 3.85 & 0.09 & 42.21 & 0.00 & ***\\ 
&  density & 0.01 & 0.12 & 0.07 & 0.94 \\ 
&  dotplot & 0.03 & 0.12 & 0.26 & 0.80 \\ 
&  histogram & 0.23 & 0.12 & 1.97 & 0.05 & . \\ [2pt]
\multicolumn{2}{l}{\bf covariates}\\
&      d & -0.23 & 0.08 & -3.02 & 0.00 & ***\\ [1pt]
&    n1$_{100}$ & 0.07 & 0.04 & 1.70 & 0.09 & .\\ [1pt]
&  ratio & -0.04 & 0.02 & -1.48 & 0.14  \\ [2pt]
\multicolumn{2}{l}{\bf interactions}\\
&  density:d & 0.11 & 0.11 & 1.02 & 0.31 \\ 
&  dotplot:d & 0.20 & 0.11 & 1.86 & 0.06 & .  \\ 
&  histogram:d & -0.01 & 0.11 & -0.09 & 0.93 \\ [1pt]
&  density:n1$_{100}$ & -0.12 & 0.06 & -2.11 & 0.03 & *\\ 
&  dotplot:n1$_{100}$ & -0.16 & 0.06 & -2.83 & 0.00 & ***\\ 
&  histogram:n1$_{100}$ & -0.05 & 0.06 & -0.93 & 0.35 \\ [1pt]
&  density:ratio & 0.04 & 0.03 & 1.18 & 0.24 \\ 
&  dotplot:ratio & 0.02 & 0.03 & 0.65 & 0.52 \\ 
&  histogram:ratio & 0.00 & 0.04 & 0.04 & 0.97 \\ 
   \hline
\\[-5pt]
   \multicolumn{5}{l}{Signif. codes:  0 `***' 0.001 `**' 0.01 `*' 0.05 `.' 0.1}
\end{tabular}}
\end{center}
\caption{\label{tbl:speed2}Results from a Generalized Linear Mixed Effects Model of (log) time to answer a lineup given design and all two-way interactions with effect size $d$, group size $n_1$, and ratio to second to first group size. Estimate and error for all terms involving $n_1$ are multiplied by a factor of 100 for comparability.
Reference group for all effects are boxplot designs. }
\end{table}

Our third response variable is again the subjective assessment of confidence level. On average participants reported a confidence in their results of  3.41 (on a five point scale with 1=lowest and 5=highest), with a standard deviation of 0.149. Modeling confidence levels with a linear mixed effects model with the same structure as before resulted in only one significant effect beyond the intercept: participants report significantly higher confidence for increased number of  points in dotplot lineups. On average an increase of 100 points leads to an increase in confidence of 0.22 (with a standard error of 0.082). This finding is significant with a $p$-value of 0.007. 
Together with the previous results, we can tell that something interesting happens in the perception of dotplots as sample sizes increase. 
*** Follow-up experiments are planned. *** do we?

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-exp2} 
   \caption{example caption}
   \label{fig:example}
\end{figure}

### 2012-03-30 experiment.tex
discussion of second experiment: time and confidence

\section{Results and Discussion}~\label{results}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{time-answer} 
   \caption{Histograms of time taken for answering lineups. On average the Euclidean design is answered faster and with higher power (percentage of correct answers). }
   \label{fig:time}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-answer} 
   \caption{Barcharts of (subjective) confidence in answering correctly for each lineup. A strongly bimodal distribution is apparent, while confidence levels for polar charts are more uniform. There are only slight (and non significant) difference between confidence levels and correctness of results.}
   \label{fig:conf}
\end{figure}

@@

@@

Overall, the results show huge differences in the power of designs between polar charts and Euclidean: Euclidean designs are significantly more powerful than polar charts, particularly so with small sample sizes. The reference line has surprisingly little influence, but it helps more for  polar charts than for barcharts,
An increase in sample size has positive impact on power (see figure \ref{fig:treatment} for an overview). Polar charts need a much bigger sample size to see an increase in power -- only at about 24\% of the original data do we see about the same power as for Euclidean charts of a sample size of 2\%.
The  changes in offset are significant -- interestingly, borderline behavior (90 and 270 degrees) does not show a difference between polar and Euclidean charts, whereas an inversion of the wave pattern (first up, then down), does show a difference. The Power of Barcharts suffers significantly  from this inversion whereas power of polar charts is unaffected. This is an unexpected finding, but is consistent throughout different lineups in the data. Figure \ref{fig:power} summarizes the results from the model: power predictions ($y$ axis) are shown by sample size ($x$ axis). The thick lines show average power by design for different shifts in wind direction. The thin lines represent power for individuals. What can be seen is the different impact of the offset by design: while  an offset of 270 degrees (the 'mountain' pattern) has the highest power in Euclidean charts, it comes out worst in polar charts.

\begin{figure*}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{predict-power} 
   \caption{Predicted Power of designs.  The thin lines and the points on $y$ axis show  variability due to individuals' abilities. The saturated lines show average predicted power for each of the designs.}
   \label{fig:power}
\end{figure*}

Time taken to answer was log transformed before the modeling process to de-emphasize the impact of very large values (up to 500 sec). The findings are consistent with correctness - time taken shows big differences between polar and Euclidean charts. The reference lines seem to increase the evaluation time, but not significantly. An increase in sample size decreases evaluation time, The inversion of the wave pattern at 180 degrees leads to a significant increase in time for Euclidean charts, but not for polar charts (at least not significantly).

 Confidence levels are measured on a five point scale --- they are subjective assessments by the participant `how certain are you'. We model confidence using the same model structure as before, i.e. using sample size and offset as covariates and including up to two-way interactions,
While there is a difference between the designs - participants reported higher confidence in dealing with the barcharts -- this is only  a trend (i.e. not significant at 5\% but below 10\%). The only significant effect on reported confidence level is the use of reference lines in polar coordinates: participants report an increase in confidence (0.31 $\pm$ 0.13, $p$ value = 0.01) when using the reference line. This, however, does not translate to a significant increase in accuracy of results, as we have seen before.

@@

Euclidean coordinates performed better when speaking of efficiency in terms of accuracy and speed. 76.92\% of the Euclidean charts shown resulted in the a correct identification of the real data while only 20.31\% of the polar charts did the same. A t-test comparing means for charts with polar coordinates versus charts with Euclidean coordinates resulted in a t statistic of 15.2013 with a p-value of 2.2e-16. Similarly, a t-test comparing means of time spent on charts with Euclidean coordinates versus charts with polar coordinates resulted in a p-value of 1.014e-11. The average of the log of time spent on each individual chart for charts with Euclidean coordinates is 3.53 minutes while it was 4.07 minutes for charts with polar coordinates. Euclidean coordinates resulted in a significantly more accurate identification of the real data set in significantly shorter time.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{turk4_time_perc_preds.pdf}  
   \caption{Values predicted from XXXX how to say itXXXX of accuracy for log of time taken and test parameter.}
   \label{accuracy_preds}
\end{figure}

Figure \ref{accuracy_preds} shows predicted accuracy levels. These predicted values were obtained by using R package lme4 and a mixed effect model explaining correct responses by type of chart and the log of time spent while accounting for different levels of accuracy for each individual who participated in the experiment. The predicted values show that there is an overall higher accuracy level for Euclidean coordinates when compared to polar coordinates. For both chart types, as the time spent increases, the predicted accuracy decreases.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   %\includegraphics[width=3in]{turk4_samplesize_correctn.pdf}  
   \caption{For each sample size for polar and Euclidean coordinates, the bars are colored according to the number of correct responses. Darker colors indicate lower accuracy levels while lighter colors indicate higher accuracy levels. }
   \label{samp_size_acc}
\end{figure}

Ideally, efficient detection of data characteristics will be possible at small sample sizes. The difficulty of the charts is largely determined by the sample size taken from the original data set. Samples of 24 \% generally result in higher accuracy as the extra information facilitates detection of a relationship. Figure \ref{accuracy_preds} shows the relationship between the number of correct responses relative to the total number of responses and how this relationship differs between Euclidean and polar coordinates. The bars in the Euclidean plot are overall a lighter color than they are in the polar plot. This indicates a higher level of accuracy at all sample sizes. For Euclidean coordinates, we can see a stair step pattern in the accuracy levels as sample size increases. Lower levels of accuracy, indicated by darker colors, become consistently less prevelant as sample size increases. The relationship between sample size and accuracy level is not as simple for polar coordinates. Sample sizes of 2\% and 4\% have very similar accuracy levels. After 6\% the stair step pattern becomes visible and similar to that of Euclidean coordinates. Sample size seems to have less of an effect on accuracy for polar coordinates than it does for Euclidean coordinates. Predicted values of the proportion of correct responses when explained by sample size, the type of chart, and the interaction between these two factors, show that there is a significant difference between the relationship between sample size and correct responses for polar and Euclidean coordinates. Indeed, the proportion of correct responses increases more rapidly as sample size increases for Euclidean coordinates than it does for polar coordinates.

The effect of a reference line on accuracy and time was not statistically significant for both types of charts. When looking at plots of the data, however, the time spent on the charts seems to be higher when there is a reference line.This is true for both Euclidean and polar charts. Also visible in the data is a slight increase in accuracy with the presence of a reference line. These characteristics can be seen in figure\ref{reflines}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   %\includegraphics[width=1.5in]{turk4_refilne_time.pdf}  
   %\includegraphics[width=1.5in]{turk4_refline_correctn.pdf}  
   \caption{The relationship between reference line and time spent (left) and the relationship between reference line and accuracy (right). Although not statistically significant, some patterns are visible.}
   \label{reflines}
\end{figure}

>>>>

% !TEX root = comparison.tex
\section{Results and Discussion}~\label{results}

@@

@@

\begin{figure}[hbtp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{time-answer} 
   \caption{Histograms of time taken for answering lineups. On average the Euclidean design is answered faster and with higher power (percentage of correct answers). }
   \label{fig:time}
\end{figure}

\begin{figure}[hbtp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{conf-answer} 
   \caption{Barcharts of (subjective) confidence in answering correctly for each lineup. A strongly bimodal distribution is apparent, while confidence levels for polar charts are more uniform. There are only slight (and non significant) difference between confidence levels and correctness of results.}
   \label{fig:conf}
\end{figure}

@@

Overall, the results show huge differences in the power of designs between polar charts and Euclidean: Euclidean designs are significantly more powerful than polar charts, particularly so with small sample sizes. 76.92\% of the Euclidean lineups shown resulted in the a correct identification of the real data while only 20.31\% of the polar charts were correct.
 The reference line has surprisingly little influence, but it helps more for  polar charts than for Euclidean charts,
An increase in sample size has positive impact on power (see figure \ref{fig:treatment} for an overview). Polar charts need a much bigger sample size to see an increase in power -- only at about 24\% of the original data do we see about the same power as for Euclidean charts of a sample size of 2\%.
The  changes in offset are significant -- interestingly, borderline behavior (90 and 270 degrees) does not show a difference between polar and Euclidean charts, whereas an inversion of the wave pattern (first up, then down), does show a difference. The power of Euclidean lineups suffers significantly  from this inversion whereas power of polar charts is unaffected. This is an unexpected finding, but is consistent throughout different lineups in the data. Figure \ref{fig:power} summarizes the results from the model: power predictions ($y$ axis) are shown by sample size ($x$ axis). The thick lines show average power by design for different shifts in wind direction. The thin lines represent power for individuals. What can be seen is the different impact of the offset by design: while  an offset of 270 degrees (the 'mountain' pattern) has the highest power in Euclidean charts, it comes out worst in polar charts.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{predict-power} 
   \caption{Predicted Power of designs.  The thin lines and the points on $y$ axis show  variability due to individuals' abilities. The saturated lines show average predicted power for each of the designs.}
   \label{fig:power}
\end{figure}

Time taken to answer was log transformed before the modeling process to de-emphasize the impact of very large values (up to 500 sec). The findings are consistent with correctness - time taken shows big differences between polar and Euclidean charts. The average of the amount of time spent on a Euclidean lineup is 3.53 minutes while it was 4.07 minutes for a polar lineup.
The reference lines seem to increase the evaluation time, but not significantly. An increase in sample size decreases evaluation time, The inversion of the wave pattern at 180 degrees leads to a significant increase in time for Euclidean charts, but not for polar charts (at least not significantly).

 Confidence levels are measured on a five point scale --- they are subjective assessments by the participant `how certain are you'. We model confidence using the same model structure as before, i.e. using sample size and offset as covariates and including up to two-way interactions,
While there is a difference between the designs - participants reported higher confidence in dealing with the Euclidean lineups -- this is only  a trend (i.e. not significant at 5\% but below 10\%). The only significant effect on reported confidence level is the use of reference lines in polar coordinates: participants report an increase in confidence (0.31 $\pm$ 0.13, $p$ value = 0.01) when using the reference line. This, however, does not translate to a significant increase in accuracy of results, as we have seen before.

 Euclidean coordinates resulted in a significantly more accurate identification of the real data set in significantly shorter time.

@@

%Euclidean coordinates performed better when speaking of efficiency in terms of accuracy and speed. 76.92\% of the Euclidean charts shown resulted in the a correct identification of the real data while only 20.31\% of the polar charts did the same. A t-test comparing means for charts with polar coordinates versus charts with Euclidean coordinates resulted in a t statistic of 15.2013 with a p-value of 2.2e-16. Similarly, a t-test comparing means of time spent on charts with Euclidean coordinates versus charts with polar coordinates resulted in a p-value of 1.014e-11. The average of the log of time spent on each individual chart for charts with Euclidean coordinates is 3.53 minutes while it was 4.07 minutes for charts with polar coordinates. Euclidean coordinates resulted in a significantly more accurate identification of the real data set in significantly shorter time.

%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=3in]{turk4_time_perc_preds.pdf}  
%   \caption{Values predicted from XXXX how to say itXXXX of accuracy for log of time taken and test parameter.}
%   \label{accuracy_preds}
%\end{figure}
%
%Figure \ref{accuracy_preds} shows predicted accuracy levels. These predicted values were obtained by using R package lme4 and a mixed effect model explaining correct responses by type of chart and the log of time spent while accounting for different levels of accuracy for each individual who participated in the experiment. The predicted values show that there is an overall higher accuracy level for Euclidean coordinates when compared to polar coordinates. For both chart types, as the time spent increases, the predicted accuracy decreases. 
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   %\includegraphics[width=3in]{turk4_samplesize_correctn.pdf}  
%   \caption{For each sample size for polar and Euclidean coordinates, the bars are colored according to the number of correct responses. Darker colors indicate lower accuracy levels while lighter colors indicate higher accuracy levels. }
%   \label{samp_size_acc}
%\end{figure}

%Ideally, efficient detection of data characteristics will be possible at small sample sizes. The difficulty of the charts is largely determined by the sample size taken from the original data set. Samples of 24 \% generally result in higher accuracy as the extra information facilitates detection of a relationship. Figure \ref{accuracy_preds} shows the relationship between the number of correct responses relative to the total number of responses and how this relationship differs between Euclidean and polar coordinates. The bars in the Euclidean plot are overall a lighter color than they are in the polar plot. This indicates a higher level of accuracy at all sample sizes. For Euclidean coordinates, we can see a stair step pattern in the accuracy levels as sample size increases. Lower levels of accuracy, indicated by darker colors, become consistently less prevalent as sample size increases. The relationship between sample size and accuracy level is not as simple for polar coordinates. Sample sizes of 2\% and 4\% have very similar accuracy levels. After 6\% the stair step pattern becomes visible and similar to that of Euclidean coordinates. Sample size seems to have less of an effect on accuracy for polar coordinates than it does for Euclidean coordinates. Predicted values of the proportion of correct responses when explained by sample size, the type of chart, and the interaction between these two factors, show that there is a significant difference between the relationship between sample size and correct responses for polar and Euclidean coordinates. Indeed, the proportion of correct responses increases more rapidly as sample size increases for Euclidean coordinates than it does for polar coordinates. 
%
%The effect of a reference line on accuracy and time was not statistically significant for both types of charts. When looking at plots of the data, however, the time spent on the charts seems to be higher when there is a reference line.This is true for both Euclidean and polar charts. Also visible in the data is a slight increase in accuracy with the presence of a reference line. These characteristics can be seen in figure\ref{reflines}.  
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   %\includegraphics[width=1.5in]{turk4_refilne_time.pdf}  
%   %\includegraphics[width=1.5in]{turk4_refline_correctn.pdf}  
%   \caption{The relationship between reference line and time spent (left) and the relationship between reference line and accuracy (right). Although not statistically significant, some patterns are visible.}
%   \label{reflines}
%\end{figure}
